COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
tried to fix contrasts

`r hypothesis1a_contrasts`

@@

interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa() +
scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
```
Johnson-Neyman intervals:

>>>>

```{r} 
apa_table(
  hypothesis1a_contrasts
)
```

@@

interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = TRUE, point.shape = TRUE,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = TRUE) + theme_apa() +
scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
```
Johnson-Neyman intervals:
